 

### 2020-10-01 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

**Wind speeds are also higher at the top of the canopy (Fig. **2x**).**
*(fill in some specifics from the NEON analysis)*
Consistent with the results from NEON sites, higher wind speed at greater heights within a forest have previously been observed in both closed canopy forests [e.g., REFS; @mcgregor_tree_nodate] and open savannas (Curtis et al. 2018).
This results in higher boundary layer conductance, *DEFINE*, for canopy leaves [@martin_boundary_1999; @robertsStomatalBoundaryLayerConductances1990].

>>>>

**Wind speeds are also higher at the top of the canopy (Fig. **2x**).**
*(fill in some specifics from the NEON analysis)*
Consistent with the results from NEON sites, higher wind speed at greater heights within a forest have previously been observed in both closed canopy forests [e.g., REFS; @mcgregor_tree_nodate] and open savannas (Curtis et al. 2018).
This results in higher boundary layer conductance ($g_{a}$) for canopy leaves. Boundary layer conductance is the thickness of air layer at the surface of the leaf through which water vapor diffuses after leaving the stomata. Large $g_{a}$ for canopy leaves results in smaller difference in $T_{air}$ and $T_{leaf}$ [@martin_boundary_1999; @robertsStomatalBoundaryLayerConductances1990].
